### 2023-03-11 README.Rmd
update the readme as so smooths do work

    Note specialist smoothers (`bs %in% c("mrf","so")`) are not currently
    supported, but univariate, *factor* and *continuous* `by`-variable smooths,
    simple random effect smooths (`bs = 're'`), factor-smooth interaction
    smooths (`bs = "fs"`), and bivariate tensor product smooths are supported,

>>>>

    Note that some specialist smoothers (`bs %in% c("mrf","sw", "sf")`) are not
    currently supported, but univariate, *factor* and *continuous* `by`-variable
    smooths, simple random effect smooths (`bs = 're'`), factor-smooth
    interaction smooths (`bs = "fs"`), constrained factor smooths (`bs = "sz"`),
    full soap film smooths (`bs = "so"`), and bivariate, trivariate, and
    quadvariate TPRS and tensor product smooths are supported,
